Automatic Hadith Graphs using Arabic Morphological Analysis

### 2011-07-28 trunk/tex/hadith.ijcnlp.tex
corrected a bug in hadith state machine
corrected bug in the traversal with caching

started editting the hadith paper

@@

@@

@@

>>>>

(modify according to hash)

@@

\subsubsection{On Test-suite Of iTree}

(report on the 90 hadith used in paper of iTree)

\subsubsection{On More Representative Test-suite}

@@

\subsection{On Unorganized hadith books}

(report results on such hadith books)

@@

(explain why successful on this problem)

(show detailed statistics and compare against that of eNarrator)

\subsection{POR Correctness}

(report recall and precision of nodes missing or those added, bc edges cannot be mistaken other than that)

(report recall and precision on the chainnodes per graphnode, that is all what retains to correctness resulting from algorithm)
